Increasing User Engagement in a Volunteer-Based Ephemeral Evolutionary Computation System

### 2017-02-17 2017-EUROPAR/Gamification/paper.tex
Adds gamification references

Recent works have been using crowdsourcing in order to train robots 
for human interaction, a representative work of this trend is that of  
Anetsberger \& Bongard \cite{anetsbergerrobots} in which they propose 
training simulated robots for the grounding of language symbols. They do this by using human 
observers that issue arbitrary commands to these robots via the web, 
providing positive or negative reinforcement in response to the
robot\'s resulting actions. For interaction, they use the Twitch 
video streaming platform where users can issue commands through the
platform's integrated chat service. Subjects were incentivized to 
interact with the system by GUI features that provided participants
with a sense of involvement with the simulation. This kind of systems
could add additional dynamics, because users can collaborate or 
even compete with each other when issuing their commands.

Most
of these papers focused on testing the system by itself as proofs of
concepts, more than on its performance or their actual influence on
the result of an evolutionary algorithm. In fact, some of them do not
even work in as a distributed computing system
\cite{EvoStar2014:jsEO}, describing the expressive capabilities of
JavaScript for evolutionary computation.

The proofs of concept described above do not go further than trying to
find out  how many users join the effort and how many the system is
able to support. In fact, systems described in
\cite{gecco07:workshop:dcor} had serious scaling issues; some of them
also tried to find out how much time was needed to find the solution
or, alternatively, how many users would be needed to be competitive
with single-user single-computer implementations of the same
algorithm. However, the latest systems try to emphasize the seamless
integration of peer and volunteer computing systems \cite{leclerc2016seamless}.

@@

\section{Gamification Technique}
\label{sec:gamification}
A definition given by Huotari  \cite{huotari2012defining} is ``Gamification is
the process by which gaming concepts are brought to the real world tasks associated with
real people''. Gamification uses game design elements out of the domain of games 
with the objective of enhancing the user's experience, engagement, productivity, 
learning, among others. Deterding et al. proposes the following definition:
 ``Gamification” is the use of game design elements in non-game contexts'' 
 \cite{deterding2011gamification}.

>>>>

Recent works have been using crowdsourcing in order to train robots 
for human interaction, a representative work of this trend is that of  
Anetsberger \& Bongard \cite{anetsbergerrobots} in which they propose 
training simulated robots for the grounding of language symbols. They do this by using human 
observers that issue arbitrary commands to these robots via the web, 
providing positive or negative reinforcement in response to the
robot\'s resulting actions. For interaction, they use the Twitch 
video streaming platform where users can issue commands through the
platform's integrated chat service. Subjects were incentivized to 
interact with the system by GUI features that provided participants
with a sense of involvement with the simulation. This kind of systems
could add additional dynamics, because users can collaborate or 
even compete with each other when issuing their commands. This approach has been called {\em social cloud} \cite{6404452}, enphasizing the fact that user participation is gamified in order to obtain the most from it \cite{7027564}.

The proofs of concept described above do not go further than trying to
find out  how many users join the effort and how many the system is
able to support. In fact, systems such as the one described in
\cite{gecco07:workshop:dcor} had serious scaling issues; some of them
also tried to find out how much time was needed to find the solution
or, alternatively, how many users would be needed to be competitive
with single-user single-computer implementations of the same
algorithm. Lately, researchers have tried to integrate volunteer as a part of a larger distributed computint effort \cite{leclerc2016seamless}. In fact, exclusive volunteer systems exhibit a certain amount of unpredictability and might be best used combined with available computing power.

@@

Next we will present the gamification technique used in this experiment.

\section{Gamification}
\label{sec:gamification}
A definition given by Huotari  \cite{huotari2012defining} is ``Gamification is
the process by which gaming concepts are brought to the real world tasks associated with
real people''. Gamification uses game design elements out of the domain of games 
with the objective of enhancing the user's experience, engagement, productivity, 
learning, among others. Deterding et al. proposes the following definition:
 ``Gamification” is the use of game design elements in non-game contexts'' 
 \cite{deterding2011gamification}.
